---
title: "R Notebook"
auth: "Nguyen Xuan Huy - FTU - HCM"
---

# ASSIGMENT SQL

## PACKAGES AND LIB

```{r}
install.packages("RJDBC")

```

```{r}
system("apt-get install -y default-jdk")

```

#### JDBC driver (ex: MySQL, PostgreSQL..)

```{r}
library(RJDBC)

```

```{r}
install.packages("DBI")

```

```{r}
install.packages("RSQLite")
```

```{r}
# Cài đặt RJDBC
install.packages("RJDBC")



```

```{r}
library(RJDBC)
```

```{r}
# Khai báo JDBC driver
drv <- JDBC("com.ibm.db2.jcc.DB2Driver", "C:/JavaR/jdbc_sqlj/db2jcc4.jar")


```

```{r}
install.packages("RMySQL")
```

```{r}
library(RSQLite)
```

## CONNECT DATABASE

```{r}

library(RJDBC)

# Khai báo file jar của MySQL Connector/J
jdbc_driver <- JDBC("com.mysql.cj.jdbc.Driver", "C:/JavaR/mysql-connector-j-9.0.0/mysql-connector-j-9.0.0.jar", identifier.quote="`")


```

```{r}
# Tạo kết nối đến Xammp
hostname <- None
port <- None
dbname <- None
username <- None
password <- None

# Khai báo url conn
url <- None

# conn đến Database
conn <- None

# Test kết nối
if (!is.null(conn)) {
  print("Kết nối OK!")
} else {
  print("Kết nối không đượci!")
}
```


## READ DATA

```{r}
# Đọc dữ liệu file CSV
file_path <- None
crime_data <- None

head(crime_data)

# Tổng quan dữ liệu (summary)
summary(crime_data)
```

## IMPORT ChicagoCrimeData.CSV TO DATABADE

```{r}
# Nhập dữ liệu trực tiếp vào MySQL (bỏ qua NA)
None

```

## TEST DATABASE (SQL)

```{r}
# Kiểm tra dữ liệu trong bảng MySQL
None

```

### Problem 1

**Total number of cases**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)


```

### Problem 2

**Total number of cases by crime type**

```{r}
query <- None

# Thực hiện Query
None

# In kết quả
print(result)
```

### Problem 3 **Total number of cases by year**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 4

**Number of cases without arrests (Non-Arrest)**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 5

**Total number of cases by community area**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 6

Number of cases with missing location information

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 7

**How does the trend of total crime incidents change over the years? Is there an increase or decrease?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)



```

### Problem 8

**Which types of crimes are increasing or decreasing over time? Is there a specific type that is particularly prevalent in recent years?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 9

**Which areas have a higher crime trend compared to others? Does this trend change over time?**

```{r}
query <- NoneORDER BY YEAR, Total_Crimes DESC;
"

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 10

**Is there a particular time of day (morning, afternoon, evening) when crimes are more likely to occur?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 11

**Is the crime trend affected by the season of the year? Which season typically has the highest number of incidents?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 12

**Which type of crime is the most prevalent in the entire dataset? What is the frequency of that type over the years?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 13

**Which locations have the highest frequency of crimes? Are there any notable patterns or hotspots?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 14

**Is there a correlation between total incidents and arrest frequency? What percentage of incidents result in arrests?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 15

**Which community areas have the highest frequency of crimes? Does this frequency change over time?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 16

**Which location descriptions have the highest frequency of crimes? Is there a difference between various location descriptions?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```

### Problem 17

**Which types of crimes are more prevalent in specific locations? Does this trend change over time?**

```{r}
query <- None

# Thực hiện Query
result <- None

# In kết quả
print(result)

```
